Spin canonical divisors of log stacky curves

### 2015-06-22 stacky_write_up/spin_cring.tex
nsf grant award number, st-donat in bib

\section{Acknowledgements}
We are grateful to David Zureick-Brown for introducing us to this
field of study, providing incredibly helpful guidance, and being an
excellent project mentor. We also thank Ken Ono and the Emory University
Number Theory REU for arranging our project and providing a great
environment for mathematical learning and collaboration. Finally, we
gratefully acknowledge that our research was financially supported by
NSF Grant \_\_\_\_\_ via the Emory University Number Theory REU. We deeply
appreciate all of the support that has made our work possible.

>>>>

\section{Acknowledgements}
We are grateful to David Zureick-Brown for introducing us to this
field of study, providing incredibly helpful guidance, and being an
excellent project mentor. We also thank Ken Ono and the Emory University
Number Theory REU for arranging our project and providing a great
environment for mathematical learning and collaboration. Finally, we
gratefully acknowledge that our research was financially supported by
NSF Grant Award Number 1250467 via the Emory University Number Theory REU.
We deeply appreciate all of the support that has made our work possible.
